The Astropy Project

### 2017-10-18 main.tex
erfa cite

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
Some of the machinery also relies on the Essential Routines of Fundamental
Astronomy (ERFA) \texttt{C} library for some of the critical underlying
transformation machinery.
\inlinecomment{EJT}{Need to create a Zenodo DOI for ERFA and then cite it here.}
% * <tjenness@lsst.org> 2017-10-16T15:53:18.375Z:
%
% I think it should mention that ERFA is related to SOFA (and cite SOFA).
%
% ^.
A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as spherical (right
ascension, declination, and distance from solar system barycenter) or Cartesian
coordinates ($x$, $y$, $z$ with the origin at ).
They can therefore change representations independent of being transformed to
other reference frames (e.g., the Galactic coordinate frame).

@@

\inlinecomment{EJT}{ERFA is likely to be referenced somewhere here. should cite the DOI as mentioned in the above ERFA refernce once it exists}

>>>>

\subsubsection{Overview}
The \package{astropy.coordinates} subpackage is designed to support representing
and transforming celestial coordinates and, new in version 2.0, velocities.
The framework heavily relies on the \package{astropy.units} subpackage, and most
inputs to objects in this subpackage are expected to be \texttt{Quantity}
objects.
Some of the machinery also relies on the Essential Routines of Fundamental
Astronomy (ERFA) \texttt{C} library for some of the critical underlying
transformation machinery \citep{erfa}, which is based on the Standards Of 
Fundamental Astronomy (SOFA) effort \citep{sofa}.

A key concept behind the design of this subpackage is that coordinate
\textit{representations} and \textit{reference systems / frames} are independent
of one another.
For example, a set of coordinates in the International Celestial Reference
System (ICRS) reference frame could be represented as spherical (right
ascension, declination, and distance from solar system barycenter) or Cartesian
coordinates ($x$, $y$, $z$ with the origin at ).
They can therefore change representations independent of being transformed to
other reference frames (e.g., the Galactic coordinate frame).

@@

Uses ERFA \citep{erfa}...
